Synthetic data (confidentiality) checks

### 2020-08-16 mice_synthesizing/data_checks.Rmd
Adjusted cart settings for data checks.

>>>>

# Adjusted settings

```{r, cache = thomcache}
syns_adj <- data %>% 
  mice(m = 100, 
       maxit = 5,
       method = cart,
       minbucket = 3,
       cp = 1e-08,
       predictorMatrix = pred, 
       where = matrix(TRUE, nrow(data), ncol(data)),
       print = FALSE,
       seed = 123)
```

```{r}
completed_adj <- complete(syns_adj, action = "all")

completed_adj %>%
  map(function(x) bind_rows(data, x) %>% duplicated) %>%
  map_dbl(sum) %>% 
  sum # total number of duplicated rows over all 100 synthetic datasets

completed_adj %>%
  map(function(x) bind_rows(data, x) %>% duplicated) %>%
  lapply(function(x) which(x)) %>%
  unlist() - nrow(data)
```

```{r, dpi = 300, fig.fullwidth = TRUE, message = F}
completed_adj %>%
  map_dfr(function(x) x) %>%
  bind_rows(., data, .id = "Imputed") %>%
  mutate(Imputed = as.numeric(Imputed)) %>%
  select_if(is.numeric) %>%
  pivot_longer(cols = -"Imputed",
               names_to = c("Variable")) %>%
  mutate(Imputed = recode(Imputed, `1` = "Synthetic data", `2` = "Observed data")) %>%
  ggplot(., mapping = aes(x = value, fill = Imputed)) +
  geom_histogram(aes(y = ..density..), position = "dodge2", ) +
  facet_wrap(~ Variable, nrow = 3, ncol = 2, scales = "free") +
  theme_classic() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

```{r, dpi = 300, fig.fullwidth = TRUE, message = F}
completed_adj %>%
  map_dfr(function(x) x) %>%
  bind_rows(., data, .id = "Imputed") %>%
  select_if(negate(is.numeric)) %>%
  map_dfr(function(x) as.character(x)) %>%
  pivot_longer(cols = -"Imputed",
               names_to = c("Variable")) %>%
  mutate(Imputed = recode(Imputed, `1` = "Synthetic data", `2` = "Observed data")) %>%
  ggplot(., mapping = aes(x = value, fill = Imputed, group = Imputed)) +
  geom_bar(aes(y = ..prop..), position = "dodge2") +
  facet_wrap(~ Variable, nrow = 3, ncol = 2, scales = "free") +
  theme_classic() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```
